\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-10-07 manuscript.Rmd
updates

```{r dependencymanager, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(warning = F, error = F, message = F)
library(packrat)
packrat::init()
#Only use when you have added some pack
packrat::snapshot(ignore.stale=TRUE)

>>>>

```{r dependencymanager, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(warning = F, error = F, message = F)
library(packrat)
packrat::init()
#Only use when you have added some pack
#packrat::snapshot(ignore.stale=TRUE)
